\documentclass[12pt,letterpaper,sans]{moderncv}
\moderncvtheme[green]{casual}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\setlength{\hintscolumnwidth}{7em}
\recomputelengths

\firstname{Aaron}
\familyname{Cruces Cáceres}
\mobile{+56-9-7423-8157}
\email{aaroncruces@gmail.com}
\social[linkedin]{https://www.linkedin.com/in/aaroncruces/}
\social[github]{https://github.com/aaroncruces}
\title {Senior Cloud, DevOps, Linux SysAdmin, and Full Stack Developer}

\begin{document}
\makecvtitle

\section{Professional Work Experience}

\cventry{July 2023 -- Present}
{Senior Cloud Infrastructure and DevOps Engineer}
{Centro Educación Industrial y Minero, CEIM}
{\newline On-site, Antofagasta}
{\newline Technologies: Microsoft Azure, Debian Linux, Docker, Samba, GitLab, Ansible, Nginx.}
{
  \begin{itemize}
    \item Deployment of App Services and virtual machines using Microsoft Azure and local servers with Proxmox.
    \item Management of Windows Server 2022 with nested virtualization, Alma Linux, and Debian operating systems.
    \item Configuration of Docker platforms with Portainer, Nginx, IIS, and \textit{standalone} services.
    \item Creation of a storage system with hard drives as a shared folder for developers, using ZFS, TrueNAS, Samba, and virtualization with Proxmox (PCI Passthrough).
    \item Implementation of a centralized password manager Bitwarden (Vaultwarden) for managing critical information.
    \item Automation of deployments with Ansible and Bash scripts, versioned with Git.
    \item Configuration of continuous integration systems using GitLab Runners, with automated Docker container deployments via Ansible.
  \end{itemize}
}
\vspace{0.5em}

\cventry{March -- June 2023}
{Computer Science Instructor}
{Instituto Profesional IPG}
{\newline On-site}
{\newline Technologies: Microsoft Office.}
{
  \begin{itemize}
    \item Practical training in the use of Microsoft Office for students across various academic programs.
  \end{itemize}
}
\vspace{0.5em}

\cventry{March -- June 2023}
{Computer Engineer and IT Technician}
{Instituto Profesional IPG}
{\newline On-site}
{\newline Technologies: Microsoft Excel, Samba, FreeBSD, Linux (Arch, Debian).}
{
  \begin{itemize}
    \item Implementation of enterprise solutions in the student admissions office, including shared folders and backups using a FreeBSD server with Samba and ZFS (mirror).
    \item Development of solutions for data manipulation in Microsoft Excel using TypeScript.
    \item Analysis and optimization of network architecture at the collaborating school Julia Herrera Varas.
  \end{itemize}
}
\vspace{0.5em}

\cventry{June 2022 -- March 2023}
{React Web Developer and Linux Services Engineer}
{Tecnojosue}
{\newline Remote, Concepción}
{\newline Technologies: ReactJS, TypeScript, Prisma ORM, ExpressJS, Linux (Arch, Debian), Bash, BAT, Samba, Cloudflare DynDNS, Portainer-Docker.}
{
  \begin{itemize}
    \item Development of a web application for inventory management using ReactJS and TypeScript.
    \item Implementation of \textit{self-hosted} applications on Linux servers using \textit{cron-jobs}, \textit{daemons}, and Docker.
  \end{itemize}
}
\vspace{0.5em}

\cventry{September -- October 2021}
{Full Stack PHP Developer}
{Te Para Tres}
{\newline Remote, Santiago}
{\newline Technologies: PHP, VSCode, Git, XDebug, Laravel, FacturaScripts, Trello.}
{
  \begin{itemize}
    \item Maintenance and analysis of \textit{legacy} systems developed with Laravel.
    \item Integration and development of new and existing systems in the FacturaScripts plugin using PHP.
  \end{itemize}
}
\vspace{0.5em}

\cventry{May -- August 2021}
{Freelance Full Stack MERN Developer}
{TeslaDelta}
{\newline Remote, Concepción}
{\newline Technologies: TypeScript, ReactJS, ReduxJS, Webpack, NodeJS, ExpressJS, MongoDB, Bootstrap, Sass, Figma, SSH, Ngrok.}
{
  \begin{itemize}
    \item Creation of a web platform for entering, modifying, and updating inventory products with barcodes and QR codes.
  \end{itemize}
}
\vspace{0.5em}

\cventry{September -- December 2020}
{Computer Engineer}
{Moldava; Intergrade}
{\newline Lo Barnechea Municipality}
{\newline Technologies: Excel VBA, Aida64, Samba, Acronis True Image.}
{
  \begin{itemize}
    \item Automation of \textit{scraping} and \textit{parsing} of Aida64 reports using Excel VBA.
    \item Migration of operating systems, installation, and administration of software and hardware.
  \end{itemize}
}
\vspace{0.5em}

\cventry{February -- April 2020}
{Computer Engineer}
{Intergrade; Just Services}
{\newline Budget Directorate, Ministry of Finance}
{\newline Technologies: VBScript, Samba, Acronis True Image.}
{
  \begin{itemize}
    \item Automation of operating system migration processes using VBScript.
    \item Installation and administration of software and hardware.
  \end{itemize}
}
\vspace{0.5em}

\cventry{October -- November 2019}
{IT Support Technician}
{Advanced Computing Technologies}
{\newline Hospital de Urgencia y Asistencia Pública, Santiago}
{\newline Technologies: None specified.}
{
  \begin{itemize}
    \item Provision of IT support services, coordinating between medical and technical staff.
  \end{itemize}
}
\vspace{0.5em}

\cventry{August -- October 2019}
{Linux Systems Engineer and IT Technician}
{La Casa Del Notebook}
{\newline Santiago Centro}
{\newline Technologies: Clonezilla, Linux, MercadoLibre, Windows, Excel.}
{
  \begin{itemize}
    \item Administration and installation of Linux systems, hardware maintenance, and inventory control.
    \item Maintenance, repair, and sale of computer equipment.
  \end{itemize}
}
\vspace{0.5em}

\cventry{March 2017 -- November 2018}
{IT Services Engineer}
{Ecacom S.P.A.}
{\newline Molycop; Terquim}
{\newline Technologies: OpenWRT, Microsoft Office, Windows.}
{
  \begin{itemize}
    \item Provision of support services, including client relations, equipment administration, and network configuration with OpenWRT.
  \end{itemize}
}
\vspace{0.5em}

\cventry{July -- November 2016}
{Full Stack MEAN Developer}
{Escuela Netland School}
{\newline Antofagasta}
{\newline Technologies: JetBrains WebStorm, AngularJS, Bootstrap, HTML, CSS, JavaScript, NodeJS, ExpressJS, MongoDB, Yarn, Gulp, Yeoman, Trello.}
{
  \begin{itemize}
    \item Development of a web platform and Android mobile application to connect students and teachers, in a team of three engineers.
  \end{itemize}
}
\vspace{0.5em}

\cventry{March -- June 2016}
{Frontend PHP Developer}
{Escuela Netland School}
{\newline Antofagasta}
{\newline Technologies: JetBrains PhpStorm, PHP, WordPress, cPanel, HTML, CSS, JavaScript.}
{
  \begin{itemize}
    \item Creation of a web platform for communicating physical education activities, using WordPress as a CMS.
  \end{itemize}
}
\vspace{0.5em}

\cventry{January -- March 2016}
{Java Developer}
{SEREMI de Educación, Región del Biobío}
{\newline Concepción}
{\newline Technologies: Java, Eclipse, Swing, Apache POI, Excel.}
{
  \begin{itemize}
    \item Development of a form application for calculating, automating, and dispatching per diem allowances.
  \end{itemize}
}
\vspace{0.5em}

\newpage

\section{Personal Projects Experience}

\cventry{}
{Self-hosted Homelab}
{System for hosting and publishing personal websites}
{\newline Technologies: Debian, Proxmox, SSH, Docker, Portainer, Authentik, ZFS, ZSH, Bash, MariaDB, PostgreSQL}
{\newline}
{
  \begin{itemize}
    \item Creation of hard drive arrays with HBA SAS controllers and ZFS for \textit{backups} and \textit{self-hosted} services.
    \item Deployment of a Bitwarden password manager for centralized key management.
    \item Configuration of web services with Portainer, protected with Authentik and published with Traefik.
    \item Version control management using Gitea.
    \item Deployment of a multimedia server with Jellyfin and Nvidia Container Runtime.
    \item Management of container databases with Docker Networks, PostgreSQL, and MariaDB.
    \item Provision of documents and photos via NextCloud and Samba, with deduplication using \textit{rdfind}, \textit{rsync}, and \textit{scripting} in Bash.
    \item Automation of deployments with Ansible, GNU Stow, \textit{rsync}, and \textit{scripting} in Bash.
  \end{itemize}
}
\vspace{0.5em}

\cventry{}
{Linux Music Setup}
{MIDI synthesizer for musicians}
{\newline Technologies: Linux, SSH, TMUX, MIDI, Jack Audio Connection Kit, KXStudio Cadence, VST/VSTi Linux Plugins}
{\newline}
{
  \begin{itemize}
    \item Configuration of a Linux environment for music synthesis with minimal requirements and zero user configuration.
  \end{itemize}
}
\vspace{0.5em}

\cventry{}
{Windows Music Setup}
{MIDI controller setup}
{\newline Technologies: FL Studio, ASIO4All, MJOY, MidiYokeNT}
{\newline}
{
  \begin{itemize}
    \item Configuration of a Windows environment to control a MIDI setup with video game controllers.
  \end{itemize}
}
\vspace{0.5em}

\cventry{}
{3D Printed Lithophanes}
{Birthday gift}
{\newline Technologies: Autodesk Fusion 360, GIMP, LuBan3D Lithophane Creator, Autodesk MeshMixer, PrusaSlicer, Prusa MK2s}
{\newline}
{
  \begin{itemize}
    \item Creation of lithophanes for a lamp with family photos, using Fusion 360 for parametric design and a tool chain (GIMP, LuBan, MeshMixer) for image transformation, manufactured with a Prusa MK2s 3D printer.
  \end{itemize}
}
\vspace{0.5em}

\newpage

\section{Academic Background}
\cventry{2009--2017}
{Civil Engineering in Computer Science and Informatics}
{Universidad Católica del Norte}
{\newline Antofagasta, Chile}
{\newline Bachelor’s Degree in Engineering Sciences.}
{}

\section{Skills}
\begin{cvcolumns}
  \cvcolumn{Languages and Frameworks}
  {
    \begin{itemize}
      \item Bash
      \item ExpressJS
      \item JavaScript
      \item NodeJS
      \item PHP
      \item Python
      \item ReactJS
      \item SQL
      \item TypeScript
      \item ZSH
    \end{itemize}
  }
  \cvcolumn{Technologies}
  {
    \begin{itemize}
      \item Ansible
      \item Docker
      \item Git
      \item GitLab
      \item Linux (Debian)
      \item Microsoft Azure
      \item Nginx
      \item Proxmox
      \item Samba
      \item ZFS
    \end{itemize}
  }
\end{cvcolumns}

\section{English Language Proficiency}
\cvlanguage{Writing}{B2}{Fluent writing}
\cvlanguage{Reading}{C1}{Fluent reading}
\cvlanguage{Speaking}{B2}{Normal-paced conversation}
\cvlanguage{Listening}{C1}{Comprehension of videos, podcasts, and native audio conferences}

\end{document}